Regular singular Volterra equations on complex domains

### 2023-08-11 reg-sing-volterra.tex
Work on "Action on integral operators"

\textcolor{SeaGreen}{$f_0 \in F\zeta^{\tau-1} + O(\zeta^\tau)$ near $\zeta = 0$ for some non-zero constant $F$.}
\end{rmk}
\color{black}
%%To control the growth of $\solproto$ away from $\zeta = 0$, we'll assume that $\hardpart$ also satisfies {\em Condition~\eqref{cond:slow}}. Under this condition, $\solproto$ is uniformly of exponential type $\lambda_0$.\footnote{Recall that a function is of exponential type $\Lambda$ if for every $\varepsilon>0$ there is a constant $A_\varepsilon$ (which depends on $\varepsilon$) such that $|f(x)|\leq A_\varepsilon e^{\Lambda+\varepsilon} $. We instead require that there exists a uniform constant $A$ such that for every $\varepsilon>0$ the bound holds.}
The solution $\solproto$ from Theorem~\ref{thm:basic_volterra} has, at worst, a mild power-law singularity at $\zeta = 0$. With stronger constraints on $\hardpart$, we can also ensure that $\solproto$ grows at most exponentially as $|\zeta| \to \infty$. The function spaces defined in Section~\ref{fn-spaces} express both of these regularity properties.
\begin{thm}\label{thm:proto-growth}
Suppose $\hardpart$ satisfies {\em Condition~\eqref{cond:sing}}. Then, on a small enough neighborhood of $\zeta = 0$, we have $|\solproto| \lesssim |\zeta|^{\tau-1}$.

@@

Fixing a real constant $\Lambda$, let's restrict our attention to holomorphic functions on $\Omega$ which are bounded by constant multiples of $e^{\Lambda|\zeta|}$. One might describe these functions as being uniformly of exponential type $\Lambda$. They form a space $\singexp{0}{\Lambda}(\Omega)$, which we'll equip with the norm $\|f\|_{0,\Lambda} = \sup_\Omega e^{-\Lambda|\zeta|}\,|f|$. With respect to the seminorm on $\holo(\Omega)$ given by a compact set $K \subset \Omega$, the inclusion map $\singexp{0}{\Lambda}(\Omega) \hookrightarrow \holo(\Omega)$ has norm $\sup_K e^{\Lambda |\zeta|}$. That means the inclusion is continuous.
\begin{prop}\label{exp-complete}
The space $\singexp{0}{\Lambda}(\Omega)$ is complete.
\end{prop}
\begin{proof}
Take a Cauchy sequence $f_1, f_2, f_3, \ldots \in \singexp{0}{\Lambda}(\Omega)$. The inclusion map $\singexp{0}{\Lambda}(\Omega) \hookrightarrow \holo(\Omega)$ is bounded with respect to each of the seminorms on $\holo(\Omega)$ given by $|f| \mapsto \sup_K |f|$ for compact subsets $K \subset \Omega$, so our sequence is Cauchy in $\holo(\Omega)$ too. Since $\holo(\Omega)$ is complete~\cite[Proposition~3.5]{fnl-cpx-anal},\footnote{That is, a sequence which is Cauchy in each of the seminorms on $\holo(\Omega)$ will always converge in the topology of $\holo(\Omega)$, which is the coarsest topology in which all of the seminorms are continuous.} our sequence converges to a function $f$ there.

@@

%%which is effectively finite-order over $\Omega$ in the sense of Definition~\ref{fin-order}, with order at least $1 + \epsilon$ for some $\epsilon \in (0, \infty)$.
\section{Solving holomorphic Volterra equations}
\subsection{Overview}
\begin{brainstorm}
\item Explain how we're going to prove Theorem~\ref{thm:general_volterra}.
\item Roughly follow the sections. Eventual goal: make section titles match proof steps.
\begin{itemize}
\item Link to subsections during description.
\end{itemize}
\item Rough sketch of proof story:
\begin{itemize}
    \item Construct prototype solution $f_0$. Show it's in $\singexp{\tau-1}{\lambda_0}$.
    \item Show that $\softpart$ maps $f_0$ into $\singexp{\tau-1+\varepsilon}{\Lambda}$ for $\Lambda\geq\lambda_\Delta$ (see Corollary \ref{cor:pertub_f0}).
    \item Show that $\volterra$ contracts $\singexp{\rho-1}{\Lambda}$ when $\rho > \tau$ and $\Lambda$ is big enough (done in Proposition \ref{prop:get-contraction}).
    \item Use the contraction mapping theorem to prove Lemma~\ref{lem:perturbed_volterra}, and then use that lemma to prove Theorem~\ref{thm:general_volterra}.
\end{itemize}
\end{brainstorm}
\subsection{Bounds on the perturbed kernel}\label{sec:bounds on k}
 When $\hardpart$ satisfies Condition \eqref{cond:sing} and $\softpart$ satisfies Condition \eqref{cond:eps-lambda}, we can estimate the kernel $k$ near $\zeta=0$. On the one hand, we can make the kernel $\hardker$ arbitrary close to $\frac{\tau}{|\zeta(a)|}$, by letting $a,a'$ close enough to $\zeta=0$. If we choose $\varepsilon>0$, we can choose $\delta$ such that for every $\zeta(a)<\delta$ and $\zeta(a') <\delta$

\begin{align*}
    |\hardker(a,a')| &\leq \left\vert\hardker(a,a')-\frac{\tau}{\zeta(a)} \right\vert +\frac{\tau}{|\zeta(a)|}\\
    &\leq \varepsilon +\frac{\tau}{|\zeta(a)|} 
\end{align*}

On the other hand, we can make the kernel $\softker$ arbitrary small by letting $a,a'$ close enough to $\zeta=0$. Assuming $|\zeta(a)|<\delta$ and $|\zeta(a')|<\delta$, by Condition \eqref{cond:eps-lambda}

@@

Hence, collecting these results together, if $a,a'$ are close enough to $\zeta=0$, there exists a constant $\sigma>\tau$ such that

\[
    |k(a,a')|\leq \frac{\sigma}{|\zeta(a)|}
\]

We'll use this fact is Sections \ref{sec:V is a contraction} and \ref{sec:existence and uniqueness}.

@@

\color{black}

Similarly, we can estimate the kernel $k$ far from $\zeta=0$. Assuming $\hardpart$ satisfies Condition \eqref{cond:diag-basic} and $\softpart$ satisfies Condition \eqref{cond:eps-lambda}, for $|\zeta(a)|\geq \delta$ and for every $a'\in\Omega$

@@

\begin{prop}\label{prop:get-contraction}
Suppose that $\hardpart$ satisfies {\em Conditions \eqref{cond:sing}} and \eqref{cond:diag-basic}, and $\softpart$ satisfies {\em Condition \eqref{cond:eps-lambda}}. Then, for each $\rho > \tau$, we can ensure that $\volterra$ is a contraction of $\singexp{\rho-1}{\Lambda}$ by making $\Lambda$ big enough.
\end{prop}
\begin{rmk}
For the argument, we'll use, ``big enough'' always requires $\Lambda > \lambda_\Delta$, and may require $\Lambda \gg \lambda_\Delta$.
\end{rmk}
First, pick some $\sigma \in (\tau, \rho)$.\footnote{If you'd like, you can fix a choice of $\sigma$---for example, taking $\sigma = \frac{1}{2}(\tau + \rho)$.} By Conditions \eqref{cond:sing} and \eqref{cond:eps-lambda}, we can find a neighborhood $\near \subset \domain$ of $\zeta = 0$ with the property that
\begin{equation}\label{near-limit}
|k(a, a')| \le \frac{\sigma}{|\zeta(a)|}
\end{equation}
for all $a, a' \in \near$ (see Section \ref{sec:bounds on k}). By choosing a small enough positive radius $R$, we can take $\near$ to be the part of $\domain$ where $|\zeta| < R$. Complementarily, let $\far$ be the part of $\domain$ where $R \le |\zeta|$.

@@

\color{RoyalBlue}
By Theorem \ref{thm:basic_volterra} and \ref{thm:proto-growth} (proved in Section \ref{sec:construction}), there exists a function $f_0\in \singexp{\tau-1}{\lambda_0}(\Omega)$ such that $\hardpart f_0= f_0$. Hence we can solve the Volterra equation

\begin{equation}\label{eqn:volterra}
    f = \volterra f
\end{equation}

by the following \textit{ansatz}

\[ f= f_0 + f_\star\]

with $f_\star\in\singexpalg{\tau-1+\epsilon}(\Omega)$. Plugging-it in equation \eqref{eqn:volterra} we get

\begin{align*}
    f_0 + f_\star & = \hardpart\,f_0 - \softpart \,f_0 + \volterra f_\star \\
f_0 + f_\star & = f_0 + \softpart \,f_0 + \volterra f_\star \\
f_\star & = \softpart \,f_0 + \volterra f_\star
\end{align*}

Therefore, solving the equation \eqref{eqn:volterra} is equivalent to finding a fixed point $f_\star$ of the affine-linear map

\[ f_\star \mapsto \softpart\,f_0 + \volterra f_\star. \]

This follows by Lemma \ref{lem:perturbed_volterra}.
\end{proof}

@@

\subsubsection{Action on integral operators}\label{L-int-op}
%%For $\nu \in (-\infty, 1)$, the fractional integral $\partial^{\nu-1}_{x \text{ from } 0}$ is defined by
%%\[ \partial^{\nu-1}_{x,0} f(x) \defeq \frac{1}{\Gamma(1-\nu)} \int_0^x (x-x')^{-\nu} f(x')\,dx'. \]
For $\nu \in (-\infty, 1)$, the fractional integral $\partial^{\nu-1}_{\zeta, \alpha}$ is defined by
\[ [\partial^{\nu-1}_{\zeta, \alpha} f](a) := \frac{1}{\Gamma(1-\nu)} \int_{\zeta = \alpha}^a \big(\zeta(a)-\zeta\big)^{-\nu} f\,d\zeta \]
for each $a \in \domain_\alpha$.

It obeys the expected semigroup law \cite[Section  1.3]{mladenov2014advanced}
\begin{align*}
\fracderiv{\nu}{\zeta}{\alpha}\,\fracderiv{\mu}{\zeta}{\alpha} & = \fracderiv{\nu+\mu}{\zeta}{\alpha} & \nu, \mu \in (-\infty, 0),
\end{align*}
and agrees with ordinary repeated integration when $\nu$ is an integer (see equation~35 in \cite{mladenov2014advanced}).

@@

%The Riemann-Liouville fractional derivative is a left inverse of the fractional integral, in the sense that $\fracderiv{\lambda}{\zeta}{ 0}\,\fracderiv{-\lambda}{\zeta}{0}=\text{Id}$ for all $\lambda \in (0, \infty)$. This extends the semigroup law:
%\begin{align*}
%\fracderiv{\lambda}{\zeta}{0}\,\fracderiv{\mu}{\zeta}{0} & = \fracderiv{\lambda+\mu}{\zeta}{0} & \lambda \in \R \smallsetminus \{0, 1, 2, 3, \ldots\},\quad\mu \in (-\infty, 0).
%\end{align*}

Using a 2d integration argument, akin to the one in \cite[Theorem~2.39]{laplace-tfm}, one can show that if $\partial^{-\nu}_{\zeta,a} \varphi \in \singexp{\sigma}{\Lambda}(\Omega_a)$ \textcolor{orange}{[under what condition on $\varphi$? can we do this with Proposition~\ref{prop:smoothing}?]} and
\[ \laplace_{\zeta,a}\,\partial^{-\nu}_{\zeta} \varphi = z^{-\nu} \laplace_{\zeta, a} \varphi \]
for all $\nu \in (0, \infty)$. This generalizes the Laplace transform's action on derivatives: when $\varphi \in \singexp{\sigma}{\Lambda}(\Omega_a)$, you can use differentiation under the integral to show that~\cite[Theorem~1.34]{laplace-tfm}
\begin{equation}%%\label{id:L-mult}
\laplace_{\zeta,a}^\theta (\zeta^n \varphi) = \big({-\tfrac{\partial}{\partial z}}\big)^n \laplace_{\zeta,a}^\theta \varphi.
\end{equation}
for all integers $n \ge 0$ and suitable direction $\theta$.

>>>>

\textcolor{SeaGreen}{$f_0 \in F\zeta^{\tau-1} + O(\zeta^\tau)$ near $\zeta = 0$ for some non-zero constant $F$.}
\end{rmk}
\color{black}
The solution $\solproto$ from Theorem~\ref{thm:basic_volterra} has, at worst, a mild power-law singularity at $\zeta = 0$. With stronger constraints on $\hardpart$, we can also ensure that $\solproto$ grows at most exponentially as $|\zeta| \to \infty$. The function spaces defined in Section~\ref{fn-spaces} express both of these regularity properties.
\begin{thm}\label{thm:proto-growth}
Suppose $\hardpart$ satisfies {\em Condition~\eqref{cond:sing}}. Then, on a small enough neighborhood of $\zeta = 0$, we have $|\solproto| \lesssim |\zeta|^{\tau-1}$.

@@

Fixing a real constant $\Lambda$, let's restrict our attention to holomorphic functions on $\Omega$ which are bounded by constant multiples of $e^{\Lambda|\zeta|}$. One might describe these functions as being uniformly of exponential type $\Lambda$.\footnote{Recall that a function is of exponential type $\Lambda$ if for every $\varepsilon>0$ there is a constant $A_\varepsilon$ (which depends on $\varepsilon$) such that $|f(x)|\leq A_\varepsilon e^{(\Lambda+\varepsilon)|x|}$. We instead require that there exists a uniform constant $A$ such that for every $\varepsilon>0$ the bound holds.} They form a space $\singexp{0}{\Lambda}(\Omega)$, which we'll equip with the norm $\|f\|_{0,\Lambda} = \sup_\Omega e^{-\Lambda|\zeta|}\,|f|$. With respect to the seminorm on $\holo(\Omega)$ given by a compact set $K \subset \Omega$, the inclusion map $\singexp{0}{\Lambda}(\Omega) \hookrightarrow \holo(\Omega)$ has norm $\sup_K e^{\Lambda |\zeta|}$. That means the inclusion is continuous.
\begin{prop}\label{exp-complete}
The space $\singexp{0}{\Lambda}(\Omega)$ is complete.
\end{prop}
\begin{proof}
Take a Cauchy sequence $f_1, f_2, f_3, \ldots \in \singexp{0}{\Lambda}(\Omega)$. The inclusion map $\singexp{0}{\Lambda}(\Omega) \hookrightarrow \holo(\Omega)$ is bounded with respect to each of the seminorms on $\holo(\Omega)$ given by $|f| \mapsto \sup_K |f|$ for compact subsets $K \subset \Omega$, so our sequence is Cauchy in $\holo(\Omega)$ too. Since $\holo(\Omega)$ is complete~\cite[Proposition~3.5]{fnl-cpx-anal},\footnote{That is, a sequence which is Cauchy in each of the seminorms on $\holo(\Omega)$ will always converge in the topology of $\holo(\Omega)$, which is the coarsest topology in which all of the seminorms are continuous.} our sequence converges to a function $f$ there.

@@

%%which is effectively finite-order over $\Omega$ in the sense of Definition~\ref{fin-order}, with order at least $1 + \epsilon$ for some $\epsilon \in (0, \infty)$.
\section{Solving holomorphic Volterra equations}
\subsection{Overview}
\begin{brainstorm}
\item Explain how we're going to prove Theorem~\ref{thm:general_volterra}.
\item Roughly follow the sections. Eventual goal: make section titles match proof steps.
\begin{itemize}
\item Link to subsections during description.
\end{itemize}
\item Rough sketch of proof story:
\begin{itemize}
    \item Construct prototype solution $f_0$. Show it's in $\singexp{\tau-1}{\lambda_0}$.
    \item Show that $\softpart$ maps $f_0$ into $\singexp{\tau-1+\varepsilon}{\Lambda}$ for $\Lambda\geq\lambda_\Delta$ (see Corollary \ref{cor:pertub_f0}).
    \item Show that $\volterra$ contracts $\singexp{\rho-1}{\Lambda}$ when $\rho > \tau$ and $\Lambda$ is big enough (done in Proposition \ref{prop:get-contraction}).
    \item Use the contraction mapping theorem to prove Lemma~\ref{lem:perturbed_volterra}, and then use that lemma to prove Theorem~\ref{thm:general_volterra}.
\end{itemize}
\end{brainstorm}
\subsection{Bounds on the perturbed kernel}\label{sec:bounds on k}
\subsubsection{Overview}
The conditions on $\hardker$ and $\softker$ described in Sections \ref{setting:basic} and \ref{setting:perturbed} can be combined
\subsubsection{Bounds near $\zeta = 0$}
When $\hardpart$ satisfies Condition~\eqref{cond:sing} and $\softpart$ satisfies Condition~\eqref{cond:eps-lambda}, we can estimate the kernel $k$ near $\zeta=0$.

Condition~\eqref{cond:sing} doesn't stop $|\hardker(a, a')|$ from exceeding $\frac{\tau}{|\zeta(a)|}$. However, by keeping $a$ and $a'$ close to $\zeta = 0$, we can make sure that $|\hardker(a, a')|$ only exceeds $\frac{\tau}{|\zeta(a)|}$ by an arbitrariy small margin. Condition~\eqref{cond:sing} tells us that when $\delta > 0$ is small enough, there's a constant $C$ with
\[ \left| \hardker(a, a') - \frac{\tau}{\zeta(a)} \right| < C \]
whenever $|\zeta(a)| < \delta$ and $|\zeta(a')| < \delta$. It follows that
\begin{align*}
|\hardker(a,a')| &\leq \frac{\tau}{|\zeta(a)|}+\left\vert\frac{\tau}{\zeta(a)} - \hardker(a,a')\right\vert \\
&\leq \frac{\tau}{|\zeta(a)|} + C \\
&= \frac{\tau + C|\zeta(a)|}{|\zeta(a)|} \\
&\le \frac{\tau + C\delta}{|\zeta(a)|}
\end{align*}
whenever $|\zeta(a)| < \delta$ and $|\zeta(a')| < \delta$. By shrinking the radius $\delta$, we can make $C\delta$ as small as we want.
\textcolor{orange}{[\ldots]}

\color{RoyalBlue}
On the one hand, we can make the kernel $\hardker$ arbitrary close to $\frac{\tau}{|\zeta(a)|}$, by keeping $a,a'$ close enough to $\zeta=0$. If we choose $\varepsilon>0$, we can choose $\delta$ such that for every $\zeta(a)<\delta$ and $\zeta(a') <\delta$
\begin{align*}
|\hardker(a,a')| &\leq \left\vert\hardker(a,a')-\frac{\tau}{\zeta(a)}\right\vert +\frac{\tau}{|\zeta(a)|}\\
&\leq \varepsilon +\frac{\tau}{|\zeta(a)|}.
\end{align*}
\textcolor{magenta}{[Condition~\eqref{cond:sing} doesn't say that for every $\varepsilon > 0$, this bound holds for small enough $\delta > 0$. It only says that when $\delta > 0$ is small enough, the bound holds for some $\varepsilon$]}
\color{black}

Under Condition~\eqref{cond:eps-lambda}, we can make $|\softker(a, a')|$ as small as we want by keeping $a$ and $a'$ close to $\zeta = 0$. The condition tells us that
\[ \big| \softker(a, a') \big| \lesssim\frac{|\zeta(a)-\zeta(a')|^\epsilon}{|\zeta(a)|}\,e^{\lambda_\Delta|\zeta(a)-\zeta(a')|}\]
over all $a, a' \in \domain$, which means that
\[ \big| \softker(a, a') \big| \lesssim\frac{(2\delta)^\epsilon}{|\zeta(a)|}\,e^{\lambda_\Delta(2\delta)}\]
over all $a, a' \in \domain$ with $|\zeta(a)| < \delta$ and $|\zeta(a')| < \delta$.
\par\color{RoyalBlue}
Condition \eqref{cond:eps-lambda} gives a bound on $\softker$, which can be made arbitrarily small by keeping $a,a'$ close enough to $\zeta=0$. Indeed, assuming $|\zeta(a)|<\delta$ and $|\zeta(a')|<\delta$

@@

Hence, collecting these results together, we can find a constant $\sigma>\tau$ such that for $a,a'$ close enough to $\zeta=0$

\[
    |k(a,a')|\leq \frac{\sigma}{|\zeta(a)|}
\]
We'll use this fact in Sections \ref{sec:V is a contraction} and \ref{sec:existence and uniqueness}.

@@

\color{black}
\subsubsection{Bounds far from the diagonal}
Similarly, we can estimate the kernel $k$ far from $\zeta=0$. Assuming $\hardpart$ satisfies Condition \eqref{cond:diag-basic} and $\softpart$ satisfies Condition \eqref{cond:eps-lambda}, for $|\zeta(a)|\geq \delta$ and for every $a'\in\Omega$

@@

\begin{prop}\label{prop:get-contraction}
Suppose that $\hardpart$ satisfies {\em Conditions \eqref{cond:sing}} and \eqref{cond:diag-basic}, and $\softpart$ satisfies {\em Condition \eqref{cond:eps-lambda}}. Then, for each $\rho > \tau$, we can ensure that $\volterra$ is a contraction of $\singexp{\rho-1}{\Lambda}$ by making $\Lambda$ big enough.
\end{prop}
\begin{rmk}
For the argument, we'll use, ``big enough'' always requires $\Lambda > \lambda_\Delta$, and may require $\Lambda \gg \lambda_\Delta$.
\end{rmk}
First, pick some $\sigma \in (\tau, \rho)$.\footnote{If you'd like, you can fix a choice of $\sigma$---for example, taking $\sigma = \frac{1}{2}(\tau + \rho)$.} By Conditions \eqref{cond:sing} and \eqref{cond:eps-lambda}, we can find a neighborhood $\near \subset \domain$ of $\zeta = 0$ with the property that
\begin{equation}\label{near-limit}
|k(a, a')| \le \frac{\sigma}{|\zeta(a)|}
\end{equation}
for all $a, a' \in \near$ (see Section~\ref{sec:bounds on k}). By choosing a small enough positive radius $R$ \textcolor{orange}{[let's choose $R$ or $\delta$ to use both here and in Section~\ref{sec:bounds on k}]}, we can take $\near$ to be the part of $\domain$ where $|\zeta| < R$. Complementarily, let $\far$ be the part of $\domain$ where $R \le |\zeta|$.

@@

@@

\subsubsection{Action on integral operators}\label{L-int-op}
%%For $\nu \in (-\infty, 1)$, the fractional integral $\partial^{\nu-1}_{x \text{ from } 0}$ is defined by
%%\[ \partial^{\nu-1}_{x,0} f(x) \defeq \frac{1}{\Gamma(1-\nu)} \int_0^x (x-x')^{-\nu} f(x')\,dx'. \]
For $\nu \in (0, \infty)$, the fractional integral $\partial^{-\nu}_{\zeta, \alpha}$ is defined by
\[ [\partial^{-\nu}_{\zeta, \alpha} f](a) := \frac{1}{\Gamma(\nu)} \int_{\zeta = \alpha}^a \big(\zeta(a)-\zeta\big)^{\nu-1} f\,d\zeta \]
for each $a \in \domain_\alpha$.
\par\color{RoyalBlue}
For $\nu' \in (-\infty, 1)$, the fractional integral $\partial^{\nu'-1}_{\zeta, \alpha}$ is defined by \textcolor{orange}{[$-\nu = \nu'-1$ and $1-\nu = \nu'$]}
\[ [\partial^{\nu'-1}_{\zeta, \alpha} f](a) := \frac{1}{\Gamma(1-\nu')} \int_{\zeta = \alpha}^a \big(\zeta(a)-\zeta\big)^{-\nu'} f\,d\zeta \]
for each $a \in \domain_\alpha$.
\color{black}

It obeys the expected semigroup law \cite[Section~1.3]{mladenov2014advanced}
\begin{align*}
\fracderiv{-\nu}{\zeta}{\alpha}\,\fracderiv{-\mu}{\zeta}{\alpha} & = \fracderiv{-\nu-\mu}{\zeta}{\alpha} & \nu, \mu \in (0, \infty),
\end{align*}
and agrees with ordinary repeated integration when $\nu$ is an integer \cite[Equation~35]{mladenov2014advanced}.

@@

%The Riemann-Liouville fractional derivative is a left inverse of the fractional integral, in the sense that $\fracderiv{\lambda}{\zeta}{ 0}\,\fracderiv{-\lambda}{\zeta}{0}=\text{Id}$ for all $\lambda \in (0, \infty)$. This extends the semigroup law:
%\begin{align*}
%\fracderiv{\lambda}{\zeta}{0}\,\fracderiv{\mu}{\zeta}{0} & = \fracderiv{\lambda+\mu}{\zeta}{0} & \lambda \in \R \smallsetminus \{0, 1, 2, 3, \ldots\},\quad\mu \in (-\infty, 0).
%\end{align*}
For all $\nu\in (0,\infty)$, the fractional integral $\fracderiv{-\nu}{\zeta}{\alpha}$ behaves as a Volterra operator $\softpart$ and maps functions $\varphi\in\singexp{\sigma}{\Lambda}(\domain_\alpha)$ to $\fracderiv{-\nu}{\zeta}{\alpha}\varphi\in\singexp{\sigma+\nu}{\Lambda}(\domain_\alpha)$. Indeed, if $\zeta(a)\neq 0$ \textcolor{orange}{[if we want our previous results to apply for a singularity at $\zeta = \alpha$, I think we need to redefine our function spaces for that context]}

\begin{align*}
    \left[\fracderiv{-\nu}{\zeta}{\alpha} \varphi\right](a)&=\frac{1}{\Gamma(\nu)}\int_{\zeta=\alpha}^a (\zeta(a)-\zeta)^{\nu-1} \, \varphi \, d\zeta\\
    &=\frac{1}{\Gamma(\nu)}\int_{\zeta=\alpha}^a \frac{(\zeta(a)-\zeta)^{\nu-1}}{\zeta(a)\textcolor{orange}{- \alpha}}\,  \zeta(a)\, \varphi \, d\zeta\\
    &=\frac{\zeta(a)}{\Gamma(\nu)}\int_{\zeta=\alpha}^a \frac{(\zeta(a)-\zeta)^{\nu-1}}{\zeta(a)\textcolor{orange}{- \alpha}}\, \varphi \, d\zeta
\end{align*}
Define $\softker(a,a'):=\frac{(\zeta(a)-\zeta(a'))^{\nu-1}}{\zeta(a) \textcolor{orange}{- \alpha}}$, it satisfies Condition \eqref{cond:eps-lambda} with $\epsilon=\nu-1$ and $\lambda_\Delta=0$. Hence by Proposition \ref{prop:smoothing}

\[ \frac{1}{\Gamma(\nu)}\int_{\zeta=\alpha}^a \frac{(\zeta(a)-\zeta)^{\nu-1}}{\zeta(a)\textcolor{orange}{- \alpha}}\, \varphi \, d\zeta \in \singexp{\sigma+\nu-1}{\Lambda}(\domain_\alpha) \]

Multiplication by \textcolor{orange}{$\zeta - \alpha$} then maps functions in $\singexp{\sigma+\nu-1}{\Lambda}(\domain_\alpha)$ to $\singexp{\sigma+\nu}{\Lambda}(\domain_\alpha)$, as claimed. In particular, $\fracderiv{-\nu}{\zeta}{\alpha}\varphi$ admits a well defined Laplace transform along any ray $\Gamma_{\zeta,\alpha}^{\theta}\subset\domain_\alpha$. Thus, using a 2d integration argument, akin to the one in \cite[Theorem~2.39]{laplace-tfm}, one can show that 
\[ \laplace_{\zeta,\alpha}^{\theta}\,\fracderiv{-\nu}{\zeta}{\alpha} \varphi = z^{-\nu} \laplace_{\zeta, \alpha}^{\theta} \varphi \]
for all $\nu \in (0, \infty)$ and $\varphi\in\singexp{\sigma}{\Lambda}(\domain_\alpha)$ with $\sigma>-1$. This generalizes the Laplace transform's action on derivatives: when $\varphi \in \singexp{\sigma}{\Lambda}(\domain_\alpha)$ and $\sigma>-1$, you can use differentiation under the integral to show that~\cite[Theorem~1.34]{laplace-tfm}
\begin{equation}%%\label{id:L-mult}
\laplace_{\zeta,\alpha}^\theta (\zeta^n \varphi) = \big({-\tfrac{\partial}{\partial z}}\big)^n \laplace_{\zeta,\alpha}^\theta \varphi.
\end{equation}
for all integers $n \ge 0$ and suitable direction $\theta$.
